The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-09 paper.tex
update

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight\
  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc\
  with angular resolutions of 0.5 degrees\

@@

  \Cref{fig__xray_0.8keV_angle_000} shows\
  the simulated photon count rate (top)\
  in the 0.6--1.0 keV range at the present time,\
  overlaid with the red arrow representing the direction of the bipolar jet,\
  compared with the observed count rate (bottom) in the same energy bin.

@@

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{The slice of CR...}
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}

>>>>

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight\
  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc\
  with angular resolutions of 0.5 degrees\

@@

  \Cref{fig__xray_0.8keV_angle_000} shows\
  the comparison between simulated (top) and observed (bottom) all-sky map\
  in the range 0.6 -- 1.0 keV at the present time.\
  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
  constantly ejecting at an angle of $45\circ$ to the disc normal in 1.2 Myr.

% 1. The boundary of eROSITA bubbles is a shock
% 2. North Polar Spur is not shown as it is a supernova remanent near us.
% 3. Why the innermost bubbles does not appear?
  The innermost bubbles, even though high density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$ -- $10$ eV\
  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.

@@

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400 -- 500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{The slice of CR... $p_{CR}$ is much less than $p_{\text{gas}}$...}
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}
